### 2017-07-13 src/4_OnlineLearning.tex
comment section of Cross Validation

For time series forecasting, a cross-validation statistic is obtained as follows: fit the model to the data $y1,…,yt$ and let $y^t+1$ denote the forecast of the next observation. Then compute the error ($et+1∗=yt+1−y^t+1$) for the forecast observation.
Repeat step 1 for t=m,…,n−1 where m is the minimum number of observations needed for fitting the model.
Compute the MSE from $em+1∗,…,en∗$.

>>>>

%For time series forecasting, a cross-validation statistic is obtained as
%follows: fit the model to the data $y1,\dots,yt$ and let $y^t+1$ denote the forecast
%of the next observation. Then compute the error $et+1=yt+1-y^t+1$ for the
%forecast observation.  Repeat step 1 for $t=m,\dots,n−1$ where m is the minimum number
%of observations needed for fitting the model.
%Compute the MSE from $em+1∗,…,en∗$.
